Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

```{r Import GitHUb file (metada)}
read.table
```

@@

```{r }

@@

>>>>

@@

#Read phyloseq object
```{r OTU table read}

@@

#READ ME

Files downloaded from the emp ftp directory could not be reecognised a JSON or HDF5 file as required by the biomformat package and therefore could not be read in R. This is a significant problem that explains the use of a GitHub file (emp_deblur_150bp.subset_2k.rare_5000.biom").
This file was used as a test to verify the working order of certain sections of the code.

Table selected to run code ("/Users/Muriel/Downloads/emp_deblur_150bp.subset_2k.rare_5000.biom") does not feature sample data - it may be necessary to look into other files or acquire the sample data from another file using the sample references
